---
title: "Analyst: Carol Muriithi"
output: html_notebook
---


####Color coded Analysis Code

```{r}
#Carol: non-color coded
d <- read.table('gene_exp.diff',header=T,as.is=T) # reads the gene_exp file
d <- d[order(d$q_value),]   # arranging by q value ]
##d<- d[order(d$q_value),]
head(d, n=10) # number of DE for all genes
#hist(d$log2.fold_change.,breaks=100)
hist(d$log2.fold_change.,breaks=100, main = "Log2 Fold Change for All Genes",xlab = "Log2 fold change for All Genes",col = "cyan")



dev.copy(png,'all_cufflinks_fc.png')
dev.off()

d.sig <- subset(d,significant=="yes")  
#hist(d.sig$log2.fold_change.,breaks=100)
#hist(d.sig$log2.fold_change.,breaks=100, main = " Log2 fold change for 'Significant DE genes",xlab = "Log2 fold change",col = "cyan") 
hist(d.sig$log2.fold_change.,breaks=100, main = " Log2 fold change for 'Significant DE genes",xlab = "Log2 fold change",col = "cyan") 
head(d.sig, n=10) # number of SDE  genes
dev.copy(png,'sig_cufflinks_fc.png')
dev.off()


d.sig.up <- subset(d.sig,log2.fold_change.>0)
d.sig.dn <- subset(d.sig,log2.fold_change.<0)
dim(d.sig.up)
dim(d.sig.dn)

# writes to txt and csv files
write(d.sig.up$gene,"up_genes.txt") 
write(d.sig.dn$gene,"dn_genes.txt")
write(d.sig.up$gene,"up_genes.csv")
write(d.sig.dn$gene,"dn_genes.csv")

```


## Carol's non-color coded code
```{r}
d <- read.table('gene_exp.diff',header=T,as.is=T)
hist(d$log2.fold_change.,breaks=100)
dev.copy(png,'all_cufflinks_fc.png')
dev.off()

d.sig <- subset(d,significant=="yes")
hist(d.sig$log2.fold_change.,breaks=100)
dev.copy(png,'sig_cufflinks_fc.png')
dev.off()

d.sig <- d.sig[order(d.sig$q_value),]
d.sig.up <- subset(d.sig,log2.fold_change.>0)
d.sig.dn <- subset(d.sig,log2.fold_change.<0)


write(d.sig.up$gene,"up_genes.txt") 
write(d.sig.dn$gene,"dn_genes.txt")
write(d.sig.up$gene,"up_genes.csv")
write(d.sig.dn$gene,"dn_genes.csv")

```






Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

